Highlights

### 2021-03-28 Bike-share-spatial-equity/Cover-Letter.Rmd

Please find attached our paper submitted to the Virtual Special Issue in Transportation Research Part D: Transport and Environment (SI: Transportation Justice). The paper is titled "Examining spatial equity and accessibility to a public bicycle share program using a balanced floating catchment area approach". We use the city of Hamilton, Ontario in Canada as a case study. The city's public bicycle share program, Hamilton Bike Share, launched in 2015 and started an equity initiative in 2017 which included the addition of 13 stations to the program.

@@

1.	Our research contributes to the literature on the topic of equity in public bicycle share programs (PBSPs) which has received a lot of attention in North America recently. Other papers include Caspi & Noland, 2019, Hosford & Winters, 2018, Mooney et al., 2019, Qian et al., 2019, among others. The city of Hamilton is the only city in Canada with a PBSP that has an explicit equity program. This makes it an interesting place to examine how specific bike share stations added for the purpose of increasing equity have contributed to addressing horizontal and vertical inequities (see Chen et al., 2019). This case study also builds upon the findings from a recent paper by Hosford & Winters (2018) that explored who is served by PBSPs in Canada.

>>>>

Please find attached our paper submitted to the Virtual Special Issue in Transportation Research Part D: Transport and Environment (SI: Transportation Justice). The paper is titled "Examining spatial equity in accessibility to a public bicycle share program using a balanced floating catchment area approach". We use the city of Hamilton, Ontario in Canada as a case study. The city's public bicycle share program, Hamilton Bike Share, launched in 2015 and started an equity initiative in 2017 which included the addition of 13 stations to the program.

@@

1.	Our research contributes to the literature on the topic of equity in public bicycle share programs (PBSPs) which has received a lot of attention in North America recently. Recent papers on this topic include Caspi & Noland, 2019, Hosford & Winters, 2018, Mooney et al., 2019, Qian et al., 2019, among others. To the best of our knowledge, the city of Hamilton is the only city in Canada with a PBSP that has an explicit equity program. This makes it an interesting place to examine how specific bike share stations added for the purpose of increasing equity have contributed to addressing horizontal and vertical inequities (see Chen et al., 2019). This case study also builds upon the findings from a recent paper by Hosford & Winters (2018) that explored who is served by PBSPs in Canada.

### 2021-03-28 Bike-share-spatial-equity/Highlights.Rmd

* Contribution of equity stations to accessibility assessed at different thresholds

* Equity stations increase accessibility modestly for all income groups

>>>>

* Contribution of equity stations to accessibility assessed at different thresholds for walking time to stations

* Equity stations increased both horizontal and vertical accessibility, albeit only modestly
